A general Nullstellensatz for generalized spaces

### 2019-03-28 paper-qcoh.tex
typo

\begin{proof}By Lemma~\ref{lemma:spec-sim-representable}, the
functor~$\Spec(A^\sim)$ coincides with~$\yon A$. Since by assumption~$A$ is
contained in the site defining~$\Set[\TT]$, the exponential~$(U_\TT)^{\yon A}$
coincides with~$U_\TT|A$ (notation as in the proof in
Lemma~\ref{lemma:spec-sim-representable}), that is, the~$U_\TT$-algebra~$A^\sim$.
\end{proof}

>>>>

\begin{proof}By Lemma~\ref{lemma:spec-sim-representable}, the
functor~$\Spec(A^\sim)$ coincides with~$\yon A$. Since by assumption~$A$ is
contained in the site defining~$\Set[\TT]$, the exponential~$(U_\TT)^{\yon A}$
coincides with~$U_\TT|A$ (notation as in the proof in
Lemma~\ref{lemma:spec-sim-representable}), that is, with the~$U_\TT$-algebra~$A^\sim$.
\end{proof}
